Climate indicators

### 2023-02-27 DRAFT_climate_indicators.Rmd
tictoc

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)
library(ggpubr)
library(microbenchmark)
library(ncmeta)
dir <- substr(getwd(), 1,2)

@@

  temp <- stars::read_ncdf(paste(path2, var="tg"))
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  start <- ym(paste(year_temp, start_month, sep="-"))
  end <-  ym(paste(year_temp, end_month, sep="-"))
  myInterval <- interval(start, end)

  summerTemp_fullSeries <- c(temp, summerTemp_fullSeries)
  rm(temp)
}
```

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)
library(ggpubr)
library(microbenchmark)
library(tictoc)
library(ncmeta)
dir <- substr(getwd(), 1,2)

@@

  tic("init")
  temp <- stars::read_ncdf(paste(path2, var="tg"))
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  start <- ym(paste(year_temp, start_month, sep="-"))
  end <-  ym(paste(year_temp, end_month, sep="-"))
  myInterval <- interval(start, end)
  toc()

  tic("middle")
  temp <- temp %>%
    filter(time %within% myInterval) %>%
    st_apply(1:2, mean) %>%
    setNames(paste0("v_",year_temp))
  toc()

  tic("c")
  real_temp_summer <- c(temp, real_temp_summer)
  rm(temp)
  toc()
}
```
